\mythesistitleNOTSYNPOSIS

### 2012-01-05 src/010chap1.tex
Reordered chrono.
Added amsthm and changed theorem environs to comply.
Added atbeginend commands to space theorem environs.
Added a few \def strings.

Added placeholders for a couple of definitions.

Started editing. Intro. Added a couple of definitions.

Minor edits to comply with amsthm

Spacing hacks mostly.

Trivial.
Chapter 2 edited. See diff for details. Too many to remember. or maybe too little.

@@

The obvious first questions after being introduced to the consecutive
ones property of binary matrices are if COP can be detected
efficiently in a binary matrix and if so, can the COP permutation of
the matrix also be computed efficiently?  Recognition of COP in a
binary matrix is polynomial time solvable and the first such algorithm
was given by \cite{fg65}.  A landmark result came a few years later
when \cite{at72} discovered the families of forbidden submatrices that
prevent a matrix from having COP and most, if not all, results that
came later were based on this discovery which connected COP in binary
matrices to convex bipartite graphs. In fact, the forbidden
submatrices came as a corollary to the discovery that convex bipartite
graphs are AT-free in \cite{at72}\tnote{check}. The first linear
time algorithm for COP testing (COT) was invented by \cite{bl76} using
a data structure called PQ trees.  Since then several COT algorithms
have been invented -- some of which involved variations of PQ trees
\cite{mm96,wlh01,mcc04}, some involved set theory and ICPIA
\cite{wlh02,nsnrs09}, parallel COT algorithms\cite{as95,bs03,ly91} and
certifying algorithms\cite{mcc04}.

@@

\section{********* Application of COP in Areas of Graph Theory and
  Algorithms}
\label{sec:appcopGTA}

\subsection{********* COP in Relational Database Model}
\label{sec:apprdbm}
\tnote{(set systems theme)}

\subsection{********* COP in Graph Isomorphism}
\label{sec:appgraphiso}
\tnote{(canonization theme)}

\subsection{********* Certifying Algorithms}
\label{sec:appcertalgo}
\tnote{ (certification McC04 theme)}

>>>>

\begin{definition}{\emph{\Cop}}
  \tnote[important]{define cop here. refer to it in chap 2 or
    duplicate it using slash def }
  \begin{enumerate}
  \item \Cop
  \item Strong \cop
  \item \Cop order or \cop permutation
  \end{enumerate}
\end{definition}

\begin{figure}[t] %[htbp]
  \centering
  {\figtabsize
    \begin{tabular}[h]{l|lcccl}
      $M_1$: & $M_1'$: &&&& $M_2$:\\
      &&&&&\\
      \begin{tabular}[h]{llll}
        $c_1$ & $c_2$ &$c_3$ &$c_4$\\
        &&&\\
        \un & 0   & \un & 0\\
        0   & \un & 0   & \un \\
        \un & 0   & 0   & \un
      \end{tabular}
      &
      \begin{tabular}[h]{llll}
        $c_3$ &$c_1$ &$c_4$& $c_2$\\
        &&&\\
        \un & \un & 0 & 0\\
        0 & 0 & \un & \un \\
        0 & \un & \un & 0
      \end{tabular}
      &&&&
      \begin{tabular}[h]{llll}
        $d_1$ & $d_2$ &$d_3$ &$d_4$\\
        % &&&\\
        &&&\\
        \un & \un & 0 & 0\\
        0 & \un & \un & 0 \\
        0 & \un & 0 & \un 
      \end{tabular}
    \end{tabular}
  }

  \caption[\figtabsize Matrices with and without COP.]{\figtabsize
    Matrices with and without COP. $M_1$ has COP because by permuting
    its columns, $c_1$-$c_4$, one can obtain $M_1'$ where the {\un}s
    in each row are consecutive. $M_2$, however, does not have COP
    since no permutation of its columns, $d_1$-$d_4$, will arrange
    {\un}s in each row consecutively \cite{d08phd}.}

  \label{fig:cop-matrix}
\end{figure}

\begin{definition}{\emph{\Crop}}
  \tnote[important]{define circ1 here. refer to it in chap 2 or
    duplicate it using slash def }
\end{definition}

\begin{definition}{\emph{Binary matrix}}
  Let $M$ be an $n \times m$ matrix. $m_{i,j}$ denotes its $(i,j)$th
  element, i.e. element at $i$th row and $j$th column. $M$ is a binary
  matrix if each of its element is 0 or \un.
  In other words, for all $i \in [n]$ and $j \in [m]$, $m_{i,j} \in
  \{0, \un\}$ 
\end{definition}

@@

The obvious first questions after being introduced to the consecutive
ones property of binary matrices are if COP can be detected
efficiently in a binary matrix and if so, can the COP permutation of
the matrix also be computed efficiently?  Recognition of COP in a
binary matrix is polynomial time solvable and the first such algorithm
was given by \cite{fg65}.  A landmark result came a few years later
when \cite{at72} discovered the families of forbidden submatrices that
prevent a matrix from having COP and most, if not all, results that
came later were based on this discovery which connected COP in binary
matrices to convex bipartite graphs. In fact, the forbidden
submatrices came as a corollary to the discovery that convex bipartite
graphs are AT-free on at least one of the partitions in
\cite{at72}\tnote{check the real meaning of AT FREE. }. The first linear
time algorithm for COP testing (COT) was invented by \cite{bl76} using
a data structure called PQ trees.  Since then several COT algorithms
have been invented -- some of which involved variations of PQ trees
\cite{mm96,wlh01,mcc04}, some involved set theory and ICPIA
\cite{wlh02,nsnrs09}, parallel COT algorithms\cite{as95,bs03,ly91} and
certifying algorithms\cite{mcc04}.

@@

\section{Application of COP in Areas of Graph Theory and
  Algorithms}
\label{sec:appcopGTA}

\temptext{Combine COP in Relational Database Model + COP in Graph
  Isomorphism + Certifying Algorithms}

%\subsection{COP in Relational Database Model}
\label{sec:apprdbm}
\tnote{(set systems theme)}

%\subsection{}
\label{sec:appgraphiso}
\tnote{(canonization theme)}

%\subsection{}
\label{sec:appcertalgo}
\tnote{ (certification McC04 theme)}
